Hydraulic bore interaction with a column - A comparison between the solution of the shallow equation and experimental results

### 2015-03-12 doc/paper/paper.tex

\qijnp &= \qijn - \dtdx (\apdqimj^n + \amdqiphj^n) - \dtdy (\bpdqimj^n + \bmdqiphj^n)\\
       &-\dtdx (\tFiphj^n - \tFimhj^n) - \dtdy (\tGijph^n - \tGijmh^n)

@@

>>>>

\qijnp &=& \qijn - \dtdx \left(\apdqimj^n + \amdqiphj^n\right) - \dtdy \left(\bpdqijm^n + \bmdqijph^n\right)\nono\\
       &-&\dtdx \left(\tFiphj^n - \tFimhj^n\right) - \dtdy \left(\tGijph^n - \tGijmh^n\right)

@@

In the f-wave approache the flux is decomposed the following way
f(\qi) -f(\qim) = \psum \WZ_{i-1/2}^p = \psum \beta^p_{i-1/2}r^p_{i-1/2}
where we write this in one dimensional form since one dimensional Riemann solvers are used.
Instead of waves $\W$ representing the jump in $Q$ we have now waves $\WZ$ representing jumps in the flux. The fluctuations are defined as
\amdqimh = \sum_{p:s^p_{i-1/2}<0} \WZ_{i-1/2}^p  \quad \text{and} \quad  \apdqimh = \sum_{p:s^p_{i-1/2}>0} \WZ_{i-1/2}^p  
for the shallow water equations we are going to have
\begin{bmatrix}
H_i - H_{i-1}\\
HU_i - HU_{i-1}\\
\varphi(\qi) - \varphi(\qim) \\
B_i - B_{i-1}\\
\end{bmatrix}
= \sum_{p=0}^3 \alpha^p_{i-1/2}w^p_{i-1/2}
where $\varphi (q) = (hu^2 +\frac{1}{2}gh^2)$ is the momentum flux and $B_i$ and $B_{i-1}$ are cell-averaged approximations of the bathymetry of the respective cell.
